---
title: "README"
output: html_document
---

```{r library}
library(tidyverse)
library(rmsfuns)
library(lubridate)
library(broom)
library(rugarch)
library(rmgarch)
library(tbl2xts)
```
 


# Aim

The aim of this paper is to find the best hedge for a Rand depreciation

# Techniques used

We will use a parametric (DCC) and a non-parametric measure of a hedge (stratifying the data set)

# Data

## Data Prep

First we loaded the data ReturnsData and ETFs.

```{r Code for loading data}


etfs <-
  readRDS("data/AllFunds.rds") %>% tbl_df()

data_original <-
  readRDS("data/SA_Rand_Returns.rds")


spots <-
  readRDS("data/Spots.rds")

# Removing weekends
spots <- 
  spots %>% 
  mutate(Days = format(date, "%A")) %>% filter(!Days %in% c("Saturday", "Sunday") ) %>% select(-Days)
  
```


After this, we calculated the (simple) returns (to match the AllFunds data) and merged data

```{r Calculating returns and merging datasets}

N_Capping <- 30 # Parameter that trims the universe set. Focus, e.g., on the top 80 stocks by Market Cap.

ETFReturns <-
  etfs %>% group_by(Ticker) %>% 
  rename("TRI" = TOT_RETURN_INDEX_NET_DVDS) %>% 
  mutate(Return = TRI / lag(TRI)-1) %>% ungroup()

SAData_Returns <-   
  data_original %>% 
  filter(Universe == "JALSHAll") %>% 
  mutate(Return = coalesce(Return, 0) ) %>%   # To make NA's zero - check whether this fits in to your study / makes sense --> motivate.
  ungroup() %>% select(date, Ticker, BICS_LEVEL_1_SECTOR_NAME, Market.Cap, Return) %>% 
  group_by(date) %>% 
  arrange(date, Market.Cap) %>% 
  top_n(N_Capping, "Market.Cap") %>% ungroup()

# Caluclating returns for USDZAR:

usdzar <- 
  spots %>% group_by(Spot) %>% 
  mutate(Return = Value/lag(Value)-1) %>%  
  filter(Spot == "ZAR_Spot") %>% 
  ungroup()


# Merging datasets:
mergeddataset <- 
  bind_rows(
    ETFReturns %>% select(date, Ticker, Return),
    SAData_Returns %>% select(date, Ticker, Return),
    usdzar %>% rename("Ticker" = Spot) %>% select(date, Ticker, Return)
  )


# Dlog Returns:
mergeddataset <- 
mergeddataset %>% arrange(date) %>% group_by(Ticker) %>% mutate(Return = coalesce(Return, 0)) %>% 
  mutate(Index = cumprod(1+Return) ) %>% 
  mutate(DlogReturn =  log(Index) - log( lag(Index))) %>% ungroup() %>% 
  mutate(DlogReturn = coalesce(DlogReturn, 0)) %>% select(-Index)

# Now choose which you want to use.

```

# Stratification

## Stratifying our data
This is the code we will use to stratify our data

```{r Stratification}

Df <- 
  usdzar %>% select(date, Return) %>% filter(date > first(date))

StratValue1 <- 0.2 # Change threshold
StratValue2 <- 0.8 # Change threshold

df_Strat <- 
  Df %>% 
  mutate(Q1 = quantile(Return, StratValue1, na.rm = TRUE), Q2 = quantile(Return, StratValue2, na.rm = TRUE)) %>% 
  mutate(ID = ifelse(Return <= Q1, "Low", 
                     ifelse(Return > Q1 & Return <= Q2 , "Medium",
                            ifelse(Return > Q2 , "High", "NA")) )) %>% ungroup() 



HighDates <- df_Strat %>% filter(ID == "High") %>% pull(date)
LowDates <- df_Strat %>% filter(ID == "Low") %>% pull(date)


# And now you can do the following e.g.:
Regression_data <-   mergeddataset

Regression_data %>% filter(date %in% HighDates)



```

# Regression Time

Code for this section follows in 'compiled code.R' to get mergeddataset. 

```{r Regressions}
zar <- usdzar %>% select("date" , "Return") %>% rename("usdzar_spot" = Return) 

Regression_data <- 
  right_join(Regression_data, zar, by = "date") %>% 
  
  filter(Ticker != "ZAR_Spot") %>% 
  filter(!is.na(Return))
  
# REGRESSION ANALYSIS
# Running multiple regressions 

  #head(Regression_data)


Regressions <- 
  Regression_data %>%
  group_by(Ticker) %>% 
  do(reg = lm(usdzar_spot ~ (Return), data = .)) 

RegressionCoeffs <- 
  Regressions %>% tidy(reg)

head(RegressionCoeffs)

# Table of best -> worst headges
hedges <- RegressionCoeffs %>%  filter(., term == "Return") %>% select(., Ticker, estimate) %>% arrange(., desc(estimate))



# Tidy output for the paper 

load_pkg("huxtable")

variable.names <- unique(Regression_data$Ticker, incomparables = FALSE) #**** WHAT SHOULD WE INCLUDE HERE? LEEU?  ****

Title <- "Regression Table"


ht <- 
  huxreg(Regressions %>% filter(Ticker %in% variable.names ) %>% 
           select(reg) %>% .[[1]], 
         statistics = c(N = "nobs", R2 = "r.squared"), 
         note = "%stars%." )

#*** This takes a while to run (1-2 mins)
for(i in 1:ncol(ht)) {
  ht[1,][[1+i]] <- variable.names[i]  
}

ht %>% 
  set_caption(Title)




```
QUESTIONS:

# DCC
QUESTIONS:
\item Can't calculate the dlog returns
\item Below is a bunch of code I tried. Has not changed the resulting error when running multifit(). Takes about 15 minutes to run, the returns an error: [Error in checkForRemoteErrors(val) : 
  one node produced an error: no applicable method for 'convergence' applied to an object of class "try-error"]. Cannot find a solution online that is relevant to what we are doing.

```{r DCC}

# Univariate GARCH specifications

# Previously you were not using spread_by explicitly:
rtn <- 
  SAData_Returns %>%
  select(date, Ticker, Return) %>% 
  tbl_xts(., spread_by = "Ticker")


# This is key. You cannot run the DCC with NAs...
 rtn[is.na(rtn)] <- 0 

 
 
uspec <-
  ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1, 1)), 
             mean.model = list(armaOrder = c(1,0), include.mean = TRUE),
             distribution.model = "sstd")

multi_univ <- multispec(replicate(ncol(rtn), uspec))

spec.dcc = dccspec(multi_univ, 
                   dccOrder = c(1, 1), 
                   distribution = 'mvnorm',
                   lag.criterion = c("AIC", "HQ", "SC", "FPE")[1],
                   model = c("DCC", "aDCC")[1]) # Change to aDCC e.g.

# D) Enable clustering for speed:
cl = makePSOCKcluster(10)


# This did not work:
# Building DCC model
multf = multifit(multi_univ, rtn, cluster = cl)  # This takes a while to run (15 mins)


# **************
# Attempt no. 2
# **************


test.2 <- SAData_Returns %>%  filter(Ticker != "BAT SJ Equity") %>% rename("Date" = date) %>% select(Date, Ticker, Return)
DCCPre <- dccPre(jmsp, include.mean = T, p = 0)


rtn <- Regression_data

#drop the first observation and corresponding date:
rtn <- rtn[-1,]
# Center the data:
rtn <- scale(rtn,center=T,scale=F) 

colnames(rtn) <- 
  colnames(rtn) %>% gsub("JSE.","",.) %>% gsub(".Close","",.)

# And clean it using Boudt's technique:
rtn <- PerformanceAnalytics::Return.clean(rtn, method = c("none", "boudt", "geltner")[2], alpha = 0.01)

## Another try ********************************************************************************

testing <- mergeddataset %>% mutate(Return = coalesce(Return, 0) ) #maybe drop tbl_xts


uspec <-
  ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1, 1)), 
             mean.model = list(armaOrder = c(1,0), include.mean = TRUE),
             distribution.model = "sstd")

multi_univ <- multispec(replicate(ncol(testing), uspec))

spec.dcc = dccspec(multi_univ, 
                   dccOrder = c(1, 1), 
                   distribution = 'mvnorm',
                   lag.criterion = c("AIC", "HQ", "SC", "FPE")[1],
                   model = c("DCC", "aDCC")[1]) # Change to aDCC e.g.

# D) Enable clustering for speed:
cl = makePSOCKcluster(10)


# This did not work:
# Building DCC model
multf = multifit(multi_univ, testing, cluster = cl)  # This takes a while to run (15 mins)

```
 


# Miscellaneous Notes


***

# Paper

## Introduction

## Methodology

## Literature Review

## Results

## Conclusion


