---
title: "README"
output: html_document
---

# Aim

The aim of this paper is to find the best hedge for a Rand depreciation

# Techniques used

We will most probably use DCC modelling
Maybe also eGARCH modelling, to compare the results to that of the DCC model

# Data

Insert the data we use here

# Packages used

Insert all the packages used here

# Miscellaneous Notes

Example1: Note when running the function, BigFunc, it takes roughly 20 minutes
Example2: I have issues having my model converge
Example3: I am stuck with code in section xxx, please check this Nico

***

# Paper

## Introduction

Here I intend introducing the paper and discussing what I want to do

## Methodology

# source my functions (short handle to insert code chunk: ctrl+alt+i)

```{r Initialize}
L <- list.files("Code", full.names = true)
for (i in 1:length(L)){
  source(L[i])
}
```
# load my packages

```{r Data Import}
Data <- read_rds("Data/ReturnsData.rds")
```

```{r Returns create}

```

```{r Regressions}

```

```{r Table Output}

```

```{r Plots}

```

library(rmsfuns)
load_pkg(c("PerformanceAnalytics", "tidyverse"))


## Literature Review

## Results

## Conclusion


